---
title: "DataFest 2020 - How Will COVID-19 Affect the Occupancy in Temporary Shelters?"
author: Minsung Kim and Jonas Lee
date: June 15, 2020
output: beamer_presentation
keep_tex: yes
header-includes:
- \usepackage{multicol}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F)

```

```{r message = FALSE, echo = FALSE}
library(tidyverse)
library(ggplot2)
library(lmtest)
library(kableExtra)
#reading the csv
shelterData <- read.csv("https://raw.githubusercontent.com/alexminsung/ISSC/master/data/Daily%20shelter%20occpancy%20current.csv?token=APUVSRCQBS7QDHDGTMGCLMS65JGQU")
attach(shelterData)

# list of shelters to use later
target <- c("Cornerstone Place", "Fred Victor Centre", "St. Simon's Shelter Inc.",
            "The Scott Mission Inc.")

# filters the data for use of comparing the relationship between COVID-19 cases and occupancy numbers in shelters
shelterByCovid <- shelterData %>%
  filter(as.character(ORGANIZATION_NAME) %in% target)

```

## Changes in Percentage since COVID-19 Lockdown


\begin{multicols}{2}

  \null \vfill

```{r message = FALSE, echo = FALSE, out.width= "100%"}

# filters the data to include only Men and Women observations. Such measurements were taken because they made up most of the 
# observations and also to better illustrate a trend.
shelterData %>%
  filter(as.character(SECTOR) == "Women" & as.character(OCCUPANCY_DATE) > "2020-03-17T00:00:00") %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = relaFreq, color = SHELTER_NAME)) + geom_point() + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) + 
  labs(title = "Shelters Occupancy to Capacity Percent by Organizations (Women)", x = "Occupancy Date", y = "Relative Frequency", 
       colour = "Shelter Names")
  
shelterData %>%
  filter(as.character(SECTOR) == "Men" & as.character(OCCUPANCY_DATE) > "2020-03-17T00:00:00") %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = relaFreq, color = SHELTER_NAME)) + geom_point() + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) + 
  labs(title = "Shelters Occupancy to Capacity Percent by Organizations (Men)", x = "Occupancy Date", y = "Relative Frequency", colour = "Shelter Names")


  
```

  \vfill \null

 \columnbreak

  \null \vfill
  \begin{itemize}
    \item The data shown starts from the day when Ontario was declared to be at a state of emergency (March 17).
    \item Some shelters show a downward trend while others remain stable
  \end{itemize}
  \vfill \null
\end{multicols}

## Are COVID-19 and Number of Occupancies Correlated?

\begin{multicols}{2}

  \null \vfill

```{r echo = FALSE, out.width= "120%"}

# recorded dates for COVID-19 cases exceeding 20 in shelters 
importantDates <- c('2020-04-09T00:00:00', '2020-04-16T00:00:00', '2020-04-30T00:00:00', '2020-04-09T00:00:00',
                    '2020-05-14T00:00:00', '2020-05-16T00:00:00', '2020-05-22T00:00:00')

# creates a graph to showcase the correlation in some of the shelters
shelterByCovid %>%
  filter(as.character(OCCUPANCY_DATE) > "2020-03-017T00:00:00") %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + geom_point() + 
  facet_wrap(~ORGANIZATION_NAME) +
  geom_vline(xintercept = importantDates, color= "black", linetype="dashed") + 
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) + 
  labs(title = "Shelters Occupancy Count by Organizations", x = "Occupancy Date",
       y = "Frequency", colour = "Shelter Names")
```

  \vfill \null

  \columnbreak

  \null \vfill
  \begin{itemize}
    \item Drop in occupancy numbers coincides with the reported date of an outbreak within a shelter
    \item Could be explained by two reasons:
    \begin{enumerate}
     \item The shelter experiencing a drop is the shelter reporting an outbreak
     \item Residents in other shelters are leaving out of fear after the news of an outbreak 
   \end{enumerate}
  \end{itemize}
  \vfill \null
  
\end{multicols}
  
## The Analysis 

  
```{r echo = FALSE, out.width='200px'}

# dataset used for model
shelterDataSub <- shelterData %>%
  filter(as.character(OCCUPANCY_DATE) > "2020-03-17T00:00:00") 

# removes all NaNs caused by zero capacity values 
shelterDataSub <- shelterDataSub[!(shelterDataSub$CAPACITY == 0), ] 

# model used for comparison with another model using Likelihood Test
shelterModel2 <- glm(OCCUPANCY ~ SECTOR + CAPACITY + SHELTER_CITY, data = shelterDataSub, family = poisson(link = "log"))

# manually assigning the baseline
shelterDataSub$SECTOR <- factor(shelterDataSub$SECTOR, ordered = FALSE)
shelterDataSub$SHELTER_CITY <- factor(shelterDataSub$SHELTER_CITY, ordered = FALSE)
shelterDataSub$category <- relevel(shelterDataSub$SECTOR, 'Men')
shelterDataSub$city <- relevel(shelterDataSub$SHELTER_CITY, 'Toronto')

# model of interest
shelterModel3 <- glm(OCCUPANCY ~ category + CAPACITY*city, data = shelterDataSub, family = poisson(link = "log"))
logRate2 <- cbind(est=shelterModel3$coef, confint(shelterModel3, level=0.95))
exp(logRate2)

# likelihood test
#lmtest::lrtest(shelterModel2, shelterModel3)

```

 