---
title: "DataFest 2020 - Homeless"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r message = FALSE, echo = FALSE}
library(shiny)
library(shinydashboard)
library(tidyverse)
library(ggplot2)
library(dplyr)

#Reading the csv
shelterData <- read.csv("https://raw.githubusercontent.com/alexminsung/ISSC/master/data/Daily%20shelter%20occpancy%20current.csv?token=APUVSRCQBS7QDHDGTMGCLMS65JGQU")
attach(shelterData)

# shelterData %>% 
#   distinct(SHELTER_NAME)

# Finds all rows that starts witih "HFS"
HFS <- grep("^HFS", as.character(shelterData$SHELTER_NAME), value = TRUE)

# List of shelters with COVID19 cases
target <- c("COSTI Reception Centre", "Seaton House", HFS, "Salvation Army - Maxwell Meighen", 
            "SVDP - Mary's Home", "Robertson House")

# Filters the data by reported Covid19 cases
shelterByCovid <- shelterData %>%
  filter(as.character(SHELTER_NAME) %in% target)

```

Qs: The effects of covid19 on homeless shelters/homeless?
- but how does an increase in occupancy in shelter a impact the society (societal impact)?
- the numbers are obviously going to increase because non-essential travels are restricted and homeless are more likely to be in shelters
- there are possible health impacts...

1. try to sort the data to include 14 days period before the reported case
2. (if possible) compare it to the reported case around the region at the time of the reported case (or couple days after)
  - want to see if these shelters acted as a hotspot


```{r echo = FALSE}
#I have separated the data by sector as you suggested but even then the points are very messy. If you can think of a way to 
# improve this, then go ahead

#Filter the data by Sectors:
#Men Sector:
shelterByMen <- shelterData %>%
  filter(as.character(SECTOR) %in% target_0)



# from this we can see that men and women make up most of the data (maybe we can exclude the rest?)
cityOfToronto <- shelterData %>%
  filter(as.character(SECTOR) == "Men" & as.character(ORGANIZATION_NAME) == "City of Toronto" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  
shelterData %>%
  filter(as.character(SECTOR) == "Women") %>%
  summarise(n())


# shelterData %>%
#   filter(as.character(SECTOR) == "Co-ed" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
#   ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) +
#   geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())
# 
# shelterData %>%
#   filter(as.character(SECTOR) == "Families" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
#   ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) +     geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())


shelterData %>%
  filter(as.character(SECTOR) == "Women" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = relaFreq, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

shelterData %>%
  filter(as.character(SECTOR) == "Men" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = relaFreq, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 



# shelterData %>%
#   filter(as.character(SECTOR) == "Youth" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
#   ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) +   geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())

  
```

```{r echo = FALSE}
# this is on the side, since i wanted to see if the numbers dropped after a covid19 case was reported on some of these shelters
shelterByCovid %>%
  filter(as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00" & as.character(ORGANIZATION_NAME) == "Homes First Society"
         & as.character(SECTOR) == "Women") %>%
  mutate(log_occupancy = log(OCCUPANCY)) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + geom_point() + 
  facet_wrap(~ORGANIZATION_NAME) +
  geom_vline(aes(xintercept = '2020-04-09T00:00:00'), color="black", linetype="dashed") + 
  geom_vline(aes(xintercept = '2020-03-17T00:00:00'), color="red", linetype="dashed") +
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 
  theme(axis.text.x = element_text(angle=90, hjust=0))

```

Unlike our previous hypothesis, comparing the occupancy of Women shelters around Scarborough and Toronto have shown either a general decrease in numbers or minimal changes at best. Only one stands as an exception to this, which is the Home First Society Women's sector, where there have been a slight increase in numbers ever since Toronto's lock-down on March 17  (indicated by a red line). However, even this facility shows to illustrate a much steeper decrease around April 21st. 

I believe that this sudden decrease is likely contributed by the emergence of mass infections which occurred at the Homes First Shelter - Willowdale Welcome Center on the 9th of April. Considered as the "largest COVID-19 outbreak in the city's shelter system" by Toronto Star (https://www.thestar.com/news/gta/2020/05/24/how-a-haven-for-refugees-became-home-to-the-worst-covid-19-outbreak-in-torontos-shelter-system.html), it is no doubt that this foreboding news caught the attention of many residents in other shelters. While without solid evidence, I believe such news could have instilled fears among the residents in other Home First Society affiliated shelters, possibly providing a sufficient explanation in the sudden dip in occpancy. 


The spread characteristic of the virus could be another factor which possibly explains the decrease/little change in occupancy in shelters. As the virus is infamous for being easily contagious, it is possible that those without homes may have preferred to stay isolated from places with large crowds (i.e. shelters). This hypothesis is supported by the steadily declining numbers in occupancy at many shelters ever since COVID-19 was declared a pandemic. 



<<<<<<< HEAD


```{r echo=FALSE}
#SLR Model:
attach(shelterData)

boxplot(OCCUPANCY, main = "9839 Boxplot Boxplot", ylab = "Occupancy Number")
#From this plot it can be seen that the data is very volatile, beacuse there is a significant portion of the data outside of the whiskers

shelterData %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY)) + geom_point()

qqnorm(shelterData$OCCUPANCY, ylab = "Occupancy", main = "Hello")
qqline(shelterData$OCCUPANCY)
#From the graph it can be seen that the response variable does not follow a normal distribution, because the regression line doesn't fully encasuplate majority of the data points.


#Applying a log transformation to the Response Variable Occupancy:
#OCCUPANCY <- as.numeric(OCCUPANCY)
#Problem when converting values from 0 to lo10(0), because log10(0) give negative infintity
#qqnorm(log10(shelterData$OCCUPANCY), cex=0.5, ylab = "Log to base 10 of Sale Price", main = "9839")
#qqline(log10(shelterData$OCCUPANCY))




#APPLYING A SQRT transformation to the response variable
qqnorm(sqrt(shelterData$OCCUPANCY), cex=0.5, ylab = "Square Root of Occupancy", main = "9839 Sqrt")
qqline(sqrt(shelterData$OCCUPANCY))
#From this graph it can also be seen that the response variable "OCCUPANCY", does not follow a normal distribution, because the data does not closely follow the regression line.
```




```{r echo=FALSE}
library(shiny)
library(shinydashboard)
library(tidyverse)
library(ggplot2)

#Reading the csv
shelterData <- read.csv("https://raw.githubusercontent.com/alexminsung/ISSC/master/data/Daily%20shelter%20occpancy%20current.csv?token=APUVSRCQBS7QDHDGTMGCLMS65JGQU")
attach(shelterData)

shelterData %>% 
  distinct(SECTOR)

# Finds all rows that starts witih "HFS"
HFS <- grep("^HFS", as.character(shelterData$SHELTER_NAME), value = TRUE)

# List of men sectors
target_0 <- c("Men")

# List of women sectors
target_1 <- c("Women")

# List of co-ed sectors
target_2 <- c("Co-ed")

# List of youth sectors
target_3 <- c("Families")

# List of family sectors
target_4 <- c("Youth")

#Filter the data by Sectors:
#Men Sector:
shelterByMen <- shelterData %>%
  filter(as.character(SECTOR) %in% target_0)

#Women Sector:
shelterByWomen <- shelterData %>%
  filter(as.character(SECTOR) %in% target_1)

#Co-ed Sector:
shelterByCoed <- shelterData %>%
  filter(as.character(SECTOR) %in% target_2)

#Families Sector:
shelterByFamilies <- shelterData %>%
  filter(as.character(SECTOR) %in% target_3)

#Youth Sector:
shelterByYouth <- shelterData %>%
  filter(as.character(SECTOR) %in% target_4)

#Seeing gg-plots of each sector:
shelterByYouth %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY)) + geom_point()

#Total Occupancy of Men over the dates:
sum(shelterByMen$OCCUPANCY)

#Total Occupancy of Women over the dates:
sum(shelterByWomen$OCCUPANCY)

#Total Occupancy of Co-eds over the dates:
sum(shelterByCoed$OCCUPANCY)

#Total Occupancy of Families over the dates:
sum(shelterByFamilies$OCCUPANCY)

#Total Occupancy of Youths over the dates:
sum(shelterByYouth$OCCUPANCY)

#Total Occupancy:
sum(shelterData$OCCUPANCY)

#Now I am Subdividing the data onto a month by month basis:
#Men for a month by month basis:
men_january <- c("2020-01-01T00:00:00", "2020-01-02T00:00:00", "2020-01-03T00:00:00", "2020-01-04T00:00:00", "2020-01-05T00:00:00", "2020-01-06T00:00:00", "2020-01-07T00:00:00", "2020-01-08T00:00:00", "2020-01-09T00:00:00", "2020-01-10T00:00:00", "2020-01-11T00:00:00", "2020-01-12T00:00:00", "2020-01-13T00:00:00", "2020-01-14T00:00:00", "2020-01-15T00:00:00", "2020-01-16T00:00:00", "2020-01-17T00:00:00", "2020-01-18T00:00:00", "2020-01-19T00:00:00", "2020-01-20T00:00:00", "2020-01-21T00:00:00", "2020-01-22T00:00:00", "2020-01-23T00:00:00", "2020-01-24T00:00:00", "2020-01-25T00:00:00", "2020-01-26T00:00:00", "2020-01-27T00:00:00", "2020-01-28T00:00:00", "2020-01-29T00:00:00", "2020-01-30T00:00:00", "2020-01-31T00:00:00")

men_february <- c("2020-02-01T00:00:00", "2020-02-02T00:00:00", "2020-02-03T00:00:00", "2020-02-04T00:00:00", "2020-02-05T00:00:00", "2020-02-06T00:00:00", "2020-02-07T00:00:00", "2020-02-08T00:00:00", "2020-02-09T00:00:00", "2020-02-10T00:00:00", "2020-02-11T00:00:00", "2020-02-12T00:00:00", "2020-02-13T00:00:00", "2020-02-14T00:00:00", "2020-02-15T00:00:00", "2020-02-16T00:00:00", "2020-02-17T00:00:00", "2020-02-18T00:00:00", "2020-02-19T00:00:00", "2020-02-20T00:00:00", "2020-02-21T00:00:00", "2020-02-22T00:00:00", "2020-02-23T00:00:00", "2020-02-24T00:00:00", "2020-02-25T00:00:00", "2020-02-26T00:00:00", "2020-02-27T00:00:00", "2020-02-28T00:00:00", "2020-02-29T00:00:00")

men_march <- c("2020-03-01T00:00:00", "2020-03-02T00:00:00", "2020-03-03T00:00:00", "2020-03-04T00:00:00", "2020-03-05T00:00:00", "2020-03-06T00:00:00", "2020-03-07T00:00:00", "2020-03-08T00:00:00", "2020-03-09T00:00:00", "2020-03-10T00:00:00", "2020-03-11T00:00:00", "2020-03-12T00:00:00", "2020-03-13T00:00:00", "2020-03-14T00:00:00", "2020-03-15T00:00:00", "2020-03-16T00:00:00", "2020-03-17T00:00:00", "2020-03-18T00:00:00", "2020-03-19T00:00:00", "2020-03-20T00:00:00", "2020-03-21T00:00:00", "2020-03-22T00:00:00", "2020-03-23T00:00:00", "2020-03-24T00:00:00", "2020-03-25T00:00:00", "2020-03-26T00:00:00", "2020-03-27T00:00:00", "2020-03-28T00:00:00", "2020-03-29T00:00:00", "2020-03-30T00:00:00", "2020-03-31T00:00:00")

men_april <- c("2020-04-01T00:00:00", "2020-04-02T00:00:00", "2020-04-03T00:00:00", "2020-04-04T00:00:00", "2020-04-05T00:00:00", "2020-04-06T00:00:00", "2020-04-07T00:00:00", "2020-04-08T00:00:00", "2020-04-09T00:00:00", "2020-04-10T00:00:00", "2020-04-11T00:00:00", "2020-04-12T00:00:00", "2020-04-13T00:00:00", "2020-04-14T00:00:00", "2020-04-15T00:00:00", "2020-04-16T00:00:00", "2020-04-17T00:00:00", "2020-04-18T00:00:00", "2020-04-19T00:00:00", "2020-04-20T00:00:00", "2020-04-21T00:00:00", "2020-04-22T00:00:00", "2020-04-23T00:00:00", "2020-04-24T00:00:00", "2020-04-25T00:00:00", "2020-04-26T00:00:00", "2020-04-27T00:00:00", "2020-04-28T00:00:00", "2020-04-29T00:00:00", "2020-04-30T00:00:00")

men_may <- c("2020-05-01T00:00:00", "2020-05-02T00:00:00", "2020-05-03T00:00:00", "2020-05-04T00:00:00", "2020-05-05T00:00:00", "2020-05-06T00:00:00", "2020-05-07T00:00:00", "2020-05-08T00:00:00", "2020-05-09T00:00:00", "2020-05-10T00:00:00", "2020-05-11T00:00:00", "2020-05-12T00:00:00", "2020-05-13T00:00:00", "2020-05-14T00:00:00", "2020-05-15T00:00:00", "2020-05-16T00:00:00", "2020-05-17T00:00:00", "2020-05-18T00:00:00", "2020-05-19T00:00:00", "2020-05-20T00:00:00", "2020-05-21T00:00:00", "2020-05-22T00:00:00", "2020-05-23T00:00:00", "2020-05-24T00:00:00", "2020-05-25T00:00:00", "2020-05-26T00:00:00", "2020-05-27T00:00:00", "2020-05-28T00:00:00", "2020-05-29T00:00:00", "2020-05-30T00:00:00", "2020-05-31T00:00:00")

men_june <- c("2020-06-01T00:00:00", "2020-06-02T00:00:00", "2020-06-03T00:00:00", "2020-06-04T00:00:00", "2020-06-05T00:00:00", "2020-06-06T00:00:00", "2020-06-07T00:00:00", "2020-06-08T00:00:00")

# Filters the data by Occupancy Date
men_Jan_shelter <- shelterByMen %>%
  filter(as.character(OCCUPANCY_DATE) %in% men_january)

men_Feb_shelter <- shelterByMen %>%
  filter(as.character(OCCUPANCY_DATE) %in% men_february)

men_March_shelter <- shelterByMen %>%
  filter(as.character(OCCUPANCY_DATE) %in% men_march)

men_April_shelter <- shelterByMen %>%
  filter(as.character(OCCUPANCY_DATE) %in% men_april)

men_May_shelter <- shelterByMen %>%
  filter(as.character(OCCUPANCY_DATE) %in% men_may)

men_June_shelter <- shelterByMen %>%
  filter(as.character(OCCUPANCY_DATE) %in% men_june)



#gg-plots on a month by month basis:
men_Jan_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

men_Feb_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

men_March_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

men_April_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

men_May_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

men_June_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())


### Now The Women:
#Men for a month by month basis:
women_january <- c("2020-01-01T00:00:00", "2020-01-02T00:00:00", "2020-01-03T00:00:00", "2020-01-04T00:00:00", "2020-01-05T00:00:00", "2020-01-06T00:00:00", "2020-01-07T00:00:00", "2020-01-08T00:00:00", "2020-01-09T00:00:00", "2020-01-10T00:00:00", "2020-01-11T00:00:00", "2020-01-12T00:00:00", "2020-01-13T00:00:00", "2020-01-14T00:00:00", "2020-01-15T00:00:00", "2020-01-16T00:00:00", "2020-01-17T00:00:00", "2020-01-18T00:00:00", "2020-01-19T00:00:00", "2020-01-20T00:00:00", "2020-01-21T00:00:00", "2020-01-22T00:00:00", "2020-01-23T00:00:00", "2020-01-24T00:00:00", "2020-01-25T00:00:00", "2020-01-26T00:00:00", "2020-01-27T00:00:00", "2020-01-28T00:00:00", "2020-01-29T00:00:00", "2020-01-30T00:00:00", "2020-01-31T00:00:00")

women_february <- c("2020-02-01T00:00:00", "2020-02-02T00:00:00", "2020-02-03T00:00:00", "2020-02-04T00:00:00", "2020-02-05T00:00:00", "2020-02-06T00:00:00", "2020-02-07T00:00:00", "2020-02-08T00:00:00", "2020-02-09T00:00:00", "2020-02-10T00:00:00", "2020-02-11T00:00:00", "2020-02-12T00:00:00", "2020-02-13T00:00:00", "2020-02-14T00:00:00", "2020-02-15T00:00:00", "2020-02-16T00:00:00", "2020-02-17T00:00:00", "2020-02-18T00:00:00", "2020-02-19T00:00:00", "2020-02-20T00:00:00", "2020-02-21T00:00:00", "2020-02-22T00:00:00", "2020-02-23T00:00:00", "2020-02-24T00:00:00", "2020-02-25T00:00:00", "2020-02-26T00:00:00", "2020-02-27T00:00:00", "2020-02-28T00:00:00", "2020-02-29T00:00:00")

women_march <- c("2020-03-01T00:00:00", "2020-03-02T00:00:00", "2020-03-03T00:00:00", "2020-03-04T00:00:00", "2020-03-05T00:00:00", "2020-03-06T00:00:00", "2020-03-07T00:00:00", "2020-03-08T00:00:00", "2020-03-09T00:00:00", "2020-03-10T00:00:00", "2020-03-11T00:00:00", "2020-03-12T00:00:00", "2020-03-13T00:00:00", "2020-03-14T00:00:00", "2020-03-15T00:00:00", "2020-03-16T00:00:00", "2020-03-17T00:00:00", "2020-03-18T00:00:00", "2020-03-19T00:00:00", "2020-03-20T00:00:00", "2020-03-21T00:00:00", "2020-03-22T00:00:00", "2020-03-23T00:00:00", "2020-03-24T00:00:00", "2020-03-25T00:00:00", "2020-03-26T00:00:00", "2020-03-27T00:00:00", "2020-03-28T00:00:00", "2020-03-29T00:00:00", "2020-03-30T00:00:00", "2020-03-31T00:00:00")

women_april <- c("2020-04-01T00:00:00", "2020-04-02T00:00:00", "2020-04-03T00:00:00", "2020-04-04T00:00:00", "2020-04-05T00:00:00", "2020-04-06T00:00:00", "2020-04-07T00:00:00", "2020-04-08T00:00:00", "2020-04-09T00:00:00", "2020-04-10T00:00:00", "2020-04-11T00:00:00", "2020-04-12T00:00:00", "2020-04-13T00:00:00", "2020-04-14T00:00:00", "2020-04-15T00:00:00", "2020-04-16T00:00:00", "2020-04-17T00:00:00", "2020-04-18T00:00:00", "2020-04-19T00:00:00", "2020-04-20T00:00:00", "2020-04-21T00:00:00", "2020-04-22T00:00:00", "2020-04-23T00:00:00", "2020-04-24T00:00:00", "2020-04-25T00:00:00", "2020-04-26T00:00:00", "2020-04-27T00:00:00", "2020-04-28T00:00:00", "2020-04-29T00:00:00", "2020-04-30T00:00:00")

women_may <- c("2020-05-01T00:00:00", "2020-05-02T00:00:00", "2020-05-03T00:00:00", "2020-05-04T00:00:00", "2020-05-05T00:00:00", "2020-05-06T00:00:00", "2020-05-07T00:00:00", "2020-05-08T00:00:00", "2020-05-09T00:00:00", "2020-05-10T00:00:00", "2020-05-11T00:00:00", "2020-05-12T00:00:00", "2020-05-13T00:00:00", "2020-05-14T00:00:00", "2020-05-15T00:00:00", "2020-05-16T00:00:00", "2020-05-17T00:00:00", "2020-05-18T00:00:00", "2020-05-19T00:00:00", "2020-05-20T00:00:00", "2020-05-21T00:00:00", "2020-05-22T00:00:00", "2020-05-23T00:00:00", "2020-05-24T00:00:00", "2020-05-25T00:00:00", "2020-05-26T00:00:00", "2020-05-27T00:00:00", "2020-05-28T00:00:00", "2020-05-29T00:00:00", "2020-05-30T00:00:00", "2020-05-31T00:00:00")

women_june <- c("2020-06-01T00:00:00", "2020-06-02T00:00:00", "2020-06-03T00:00:00", "2020-06-04T00:00:00", "2020-06-05T00:00:00", "2020-06-06T00:00:00", "2020-06-07T00:00:00", "2020-06-08T00:00:00")

# Filters the data by Occupancy Date
women_Jan_shelter <- shelterByWomen %>%
  filter(as.character(OCCUPANCY_DATE) %in% women_january)

women_Feb_shelter <- shelterByWomen %>%
  filter(as.character(OCCUPANCY_DATE) %in% women_february)

women_March_shelter <- shelterByWomen %>%
  filter(as.character(OCCUPANCY_DATE) %in% women_march)

women_April_shelter <- shelterByWomen %>%
  filter(as.character(OCCUPANCY_DATE) %in% women_april)

women_May_shelter <- shelterByWomen %>%
  filter(as.character(OCCUPANCY_DATE) %in% women_may)

women_June_shelter <- shelterByWomen %>%
  filter(as.character(OCCUPANCY_DATE) %in% women_june)



#gg-plots on a month by month basis:
women_Jan_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

women_Feb_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

women_March_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

women_April_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

women_May_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

women_June_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())

### Now The Co-eds:
#Co-eds for a month by month basis:
coed_january <- c("2020-01-01T00:00:00", "2020-01-02T00:00:00", "2020-01-03T00:00:00", "2020-01-04T00:00:00", "2020-01-05T00:00:00", "2020-01-06T00:00:00", "2020-01-07T00:00:00", "2020-01-08T00:00:00", "2020-01-09T00:00:00", "2020-01-10T00:00:00", "2020-01-11T00:00:00", "2020-01-12T00:00:00", "2020-01-13T00:00:00", "2020-01-14T00:00:00", "2020-01-15T00:00:00", "2020-01-16T00:00:00", "2020-01-17T00:00:00", "2020-01-18T00:00:00", "2020-01-19T00:00:00", "2020-01-20T00:00:00", "2020-01-21T00:00:00", "2020-01-22T00:00:00", "2020-01-23T00:00:00", "2020-01-24T00:00:00", "2020-01-25T00:00:00", "2020-01-26T00:00:00", "2020-01-27T00:00:00", "2020-01-28T00:00:00", "2020-01-29T00:00:00", "2020-01-30T00:00:00", "2020-01-31T00:00:00")

coed_february <- c("2020-02-01T00:00:00", "2020-02-02T00:00:00", "2020-02-03T00:00:00", "2020-02-04T00:00:00", "2020-02-05T00:00:00", "2020-02-06T00:00:00", "2020-02-07T00:00:00", "2020-02-08T00:00:00", "2020-02-09T00:00:00", "2020-02-10T00:00:00", "2020-02-11T00:00:00", "2020-02-12T00:00:00", "2020-02-13T00:00:00", "2020-02-14T00:00:00", "2020-02-15T00:00:00", "2020-02-16T00:00:00", "2020-02-17T00:00:00", "2020-02-18T00:00:00", "2020-02-19T00:00:00", "2020-02-20T00:00:00", "2020-02-21T00:00:00", "2020-02-22T00:00:00", "2020-02-23T00:00:00", "2020-02-24T00:00:00", "2020-02-25T00:00:00", "2020-02-26T00:00:00", "2020-02-27T00:00:00", "2020-02-28T00:00:00", "2020-02-29T00:00:00")

coed_march <- c("2020-03-01T00:00:00", "2020-03-02T00:00:00", "2020-03-03T00:00:00", "2020-03-04T00:00:00", "2020-03-05T00:00:00", "2020-03-06T00:00:00", "2020-03-07T00:00:00", "2020-03-08T00:00:00", "2020-03-09T00:00:00", "2020-03-10T00:00:00", "2020-03-11T00:00:00", "2020-03-12T00:00:00", "2020-03-13T00:00:00", "2020-03-14T00:00:00", "2020-03-15T00:00:00", "2020-03-16T00:00:00", "2020-03-17T00:00:00", "2020-03-18T00:00:00", "2020-03-19T00:00:00", "2020-03-20T00:00:00", "2020-03-21T00:00:00", "2020-03-22T00:00:00", "2020-03-23T00:00:00", "2020-03-24T00:00:00", "2020-03-25T00:00:00", "2020-03-26T00:00:00", "2020-03-27T00:00:00", "2020-03-28T00:00:00", "2020-03-29T00:00:00", "2020-03-30T00:00:00", "2020-03-31T00:00:00")

coed_april <- c("2020-04-01T00:00:00", "2020-04-02T00:00:00", "2020-04-03T00:00:00", "2020-04-04T00:00:00", "2020-04-05T00:00:00", "2020-04-06T00:00:00", "2020-04-07T00:00:00", "2020-04-08T00:00:00", "2020-04-09T00:00:00", "2020-04-10T00:00:00", "2020-04-11T00:00:00", "2020-04-12T00:00:00", "2020-04-13T00:00:00", "2020-04-14T00:00:00", "2020-04-15T00:00:00", "2020-04-16T00:00:00", "2020-04-17T00:00:00", "2020-04-18T00:00:00", "2020-04-19T00:00:00", "2020-04-20T00:00:00", "2020-04-21T00:00:00", "2020-04-22T00:00:00", "2020-04-23T00:00:00", "2020-04-24T00:00:00", "2020-04-25T00:00:00", "2020-04-26T00:00:00", "2020-04-27T00:00:00", "2020-04-28T00:00:00", "2020-04-29T00:00:00", "2020-04-30T00:00:00")

coed_may <- c("2020-05-01T00:00:00", "2020-05-02T00:00:00", "2020-05-03T00:00:00", "2020-05-04T00:00:00", "2020-05-05T00:00:00", "2020-05-06T00:00:00", "2020-05-07T00:00:00", "2020-05-08T00:00:00", "2020-05-09T00:00:00", "2020-05-10T00:00:00", "2020-05-11T00:00:00", "2020-05-12T00:00:00", "2020-05-13T00:00:00", "2020-05-14T00:00:00", "2020-05-15T00:00:00", "2020-05-16T00:00:00", "2020-05-17T00:00:00", "2020-05-18T00:00:00", "2020-05-19T00:00:00", "2020-05-20T00:00:00", "2020-05-21T00:00:00", "2020-05-22T00:00:00", "2020-05-23T00:00:00", "2020-05-24T00:00:00", "2020-05-25T00:00:00", "2020-05-26T00:00:00", "2020-05-27T00:00:00", "2020-05-28T00:00:00", "2020-05-29T00:00:00", "2020-05-30T00:00:00", "2020-05-31T00:00:00")

coed_june <- c("2020-06-01T00:00:00", "2020-06-02T00:00:00", "2020-06-03T00:00:00", "2020-06-04T00:00:00", "2020-06-05T00:00:00", "2020-06-06T00:00:00", "2020-06-07T00:00:00", "2020-06-08T00:00:00")

# Filters the data by Occupancy Date
coed_Jan_shelter <- shelterByCoed %>%
  filter(as.character(OCCUPANCY_DATE) %in% coed_january)

coed_Feb_shelter <- shelterByCoed %>%
  filter(as.character(OCCUPANCY_DATE) %in% coed_february)

Coed_March_shelter <- shelterByCoed %>%
  filter(as.character(OCCUPANCY_DATE) %in% coed_march)

Coed_April_shelter <- shelterByCoed %>%
  filter(as.character(OCCUPANCY_DATE) %in% coed_april)

Coed_May_shelter <- shelterByCoed %>%
  filter(as.character(OCCUPANCY_DATE) %in% coed_may)

Coed_June_shelter <- shelterByCoed %>%
  filter(as.character(OCCUPANCY_DATE) %in% men_june)



#gg-plots on a month by month basis:
coed_Jan_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

coed_Feb_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

Coed_March_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

Coed_April_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

Coed_May_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

Coed_June_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())

### Now Families for a month by month basis:
Families_january <- c("2020-01-01T00:00:00", "2020-01-02T00:00:00", "2020-01-03T00:00:00", "2020-01-04T00:00:00", "2020-01-05T00:00:00", "2020-01-06T00:00:00", "2020-01-07T00:00:00", "2020-01-08T00:00:00", "2020-01-09T00:00:00", "2020-01-10T00:00:00", "2020-01-11T00:00:00", "2020-01-12T00:00:00", "2020-01-13T00:00:00", "2020-01-14T00:00:00", "2020-01-15T00:00:00", "2020-01-16T00:00:00", "2020-01-17T00:00:00", "2020-01-18T00:00:00", "2020-01-19T00:00:00", "2020-01-20T00:00:00", "2020-01-21T00:00:00", "2020-01-22T00:00:00", "2020-01-23T00:00:00", "2020-01-24T00:00:00", "2020-01-25T00:00:00", "2020-01-26T00:00:00", "2020-01-27T00:00:00", "2020-01-28T00:00:00", "2020-01-29T00:00:00", "2020-01-30T00:00:00", "2020-01-31T00:00:00")

Families_february <- c("2020-02-01T00:00:00", "2020-02-02T00:00:00", "2020-02-03T00:00:00", "2020-02-04T00:00:00", "2020-02-05T00:00:00", "2020-02-06T00:00:00", "2020-02-07T00:00:00", "2020-02-08T00:00:00", "2020-02-09T00:00:00", "2020-02-10T00:00:00", "2020-02-11T00:00:00", "2020-02-12T00:00:00", "2020-02-13T00:00:00", "2020-02-14T00:00:00", "2020-02-15T00:00:00", "2020-02-16T00:00:00", "2020-02-17T00:00:00", "2020-02-18T00:00:00", "2020-02-19T00:00:00", "2020-02-20T00:00:00", "2020-02-21T00:00:00", "2020-02-22T00:00:00", "2020-02-23T00:00:00", "2020-02-24T00:00:00", "2020-02-25T00:00:00", "2020-02-26T00:00:00", "2020-02-27T00:00:00", "2020-02-28T00:00:00", "2020-02-29T00:00:00")

Families_march <- c("2020-03-01T00:00:00", "2020-03-02T00:00:00", "2020-03-03T00:00:00", "2020-03-04T00:00:00", "2020-03-05T00:00:00", "2020-03-06T00:00:00", "2020-03-07T00:00:00", "2020-03-08T00:00:00", "2020-03-09T00:00:00", "2020-03-10T00:00:00", "2020-03-11T00:00:00", "2020-03-12T00:00:00", "2020-03-13T00:00:00", "2020-03-14T00:00:00", "2020-03-15T00:00:00", "2020-03-16T00:00:00", "2020-03-17T00:00:00", "2020-03-18T00:00:00", "2020-03-19T00:00:00", "2020-03-20T00:00:00", "2020-03-21T00:00:00", "2020-03-22T00:00:00", "2020-03-23T00:00:00", "2020-03-24T00:00:00", "2020-03-25T00:00:00", "2020-03-26T00:00:00", "2020-03-27T00:00:00", "2020-03-28T00:00:00", "2020-03-29T00:00:00", "2020-03-30T00:00:00", "2020-03-31T00:00:00")

Families_april <- c("2020-04-01T00:00:00", "2020-04-02T00:00:00", "2020-04-03T00:00:00", "2020-04-04T00:00:00", "2020-04-05T00:00:00", "2020-04-06T00:00:00", "2020-04-07T00:00:00", "2020-04-08T00:00:00", "2020-04-09T00:00:00", "2020-04-10T00:00:00", "2020-04-11T00:00:00", "2020-04-12T00:00:00", "2020-04-13T00:00:00", "2020-04-14T00:00:00", "2020-04-15T00:00:00", "2020-04-16T00:00:00", "2020-04-17T00:00:00", "2020-04-18T00:00:00", "2020-04-19T00:00:00", "2020-04-20T00:00:00", "2020-04-21T00:00:00", "2020-04-22T00:00:00", "2020-04-23T00:00:00", "2020-04-24T00:00:00", "2020-04-25T00:00:00", "2020-04-26T00:00:00", "2020-04-27T00:00:00", "2020-04-28T00:00:00", "2020-04-29T00:00:00", "2020-04-30T00:00:00")

Families_may <- c("2020-05-01T00:00:00", "2020-05-02T00:00:00", "2020-05-03T00:00:00", "2020-05-04T00:00:00", "2020-05-05T00:00:00", "2020-05-06T00:00:00", "2020-05-07T00:00:00", "2020-05-08T00:00:00", "2020-05-09T00:00:00", "2020-05-10T00:00:00", "2020-05-11T00:00:00", "2020-05-12T00:00:00", "2020-05-13T00:00:00", "2020-05-14T00:00:00", "2020-05-15T00:00:00", "2020-05-16T00:00:00", "2020-05-17T00:00:00", "2020-05-18T00:00:00", "2020-05-19T00:00:00", "2020-05-20T00:00:00", "2020-05-21T00:00:00", "2020-05-22T00:00:00", "2020-05-23T00:00:00", "2020-05-24T00:00:00", "2020-05-25T00:00:00", "2020-05-26T00:00:00", "2020-05-27T00:00:00", "2020-05-28T00:00:00", "2020-05-29T00:00:00", "2020-05-30T00:00:00", "2020-05-31T00:00:00")

Families_june <- c("2020-06-01T00:00:00", "2020-06-02T00:00:00", "2020-06-03T00:00:00", "2020-06-04T00:00:00", "2020-06-05T00:00:00", "2020-06-06T00:00:00", "2020-06-07T00:00:00", "2020-06-08T00:00:00")

# Filters the data by Occupancy Date
Families_Jan_shelter <- shelterByFamilies %>%
  filter(as.character(OCCUPANCY_DATE) %in% Families_january)

Families_Feb_shelter <- shelterByFamilies %>%
  filter(as.character(OCCUPANCY_DATE) %in% Families_february)

Families_March_shelter <- shelterByFamilies %>%
  filter(as.character(OCCUPANCY_DATE) %in% Families_march)

Families_April_shelter <- shelterByFamilies %>%
  filter(as.character(OCCUPANCY_DATE) %in% Families_april)

Families_May_shelter <- shelterByFamilies %>%
  filter(as.character(OCCUPANCY_DATE) %in% Families_may)

Families_June_shelter <- shelterByFamilies %>%
  filter(as.character(OCCUPANCY_DATE) %in% Families_june)



#gg-plots on a month by month basis:
Families_Jan_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

Families_Feb_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

Families_March_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

Families_April_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

Families_May_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

Families_June_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())




### Now Youths for a month by month basis:
youth_january <- c("2020-01-01T00:00:00", "2020-01-02T00:00:00", "2020-01-03T00:00:00", "2020-01-04T00:00:00", "2020-01-05T00:00:00", "2020-01-06T00:00:00", "2020-01-07T00:00:00", "2020-01-08T00:00:00", "2020-01-09T00:00:00", "2020-01-10T00:00:00", "2020-01-11T00:00:00", "2020-01-12T00:00:00", "2020-01-13T00:00:00", "2020-01-14T00:00:00", "2020-01-15T00:00:00", "2020-01-16T00:00:00", "2020-01-17T00:00:00", "2020-01-18T00:00:00", "2020-01-19T00:00:00", "2020-01-20T00:00:00", "2020-01-21T00:00:00", "2020-01-22T00:00:00", "2020-01-23T00:00:00", "2020-01-24T00:00:00", "2020-01-25T00:00:00", "2020-01-26T00:00:00", "2020-01-27T00:00:00", "2020-01-28T00:00:00", "2020-01-29T00:00:00", "2020-01-30T00:00:00", "2020-01-31T00:00:00")

youth_february <- c("2020-02-01T00:00:00", "2020-02-02T00:00:00", "2020-02-03T00:00:00", "2020-02-04T00:00:00", "2020-02-05T00:00:00", "2020-02-06T00:00:00", "2020-02-07T00:00:00", "2020-02-08T00:00:00", "2020-02-09T00:00:00", "2020-02-10T00:00:00", "2020-02-11T00:00:00", "2020-02-12T00:00:00", "2020-02-13T00:00:00", "2020-02-14T00:00:00", "2020-02-15T00:00:00", "2020-02-16T00:00:00", "2020-02-17T00:00:00", "2020-02-18T00:00:00", "2020-02-19T00:00:00", "2020-02-20T00:00:00", "2020-02-21T00:00:00", "2020-02-22T00:00:00", "2020-02-23T00:00:00", "2020-02-24T00:00:00", "2020-02-25T00:00:00", "2020-02-26T00:00:00", "2020-02-27T00:00:00", "2020-02-28T00:00:00", "2020-02-29T00:00:00")

youth_march <- c("2020-03-01T00:00:00", "2020-03-02T00:00:00", "2020-03-03T00:00:00", "2020-03-04T00:00:00", "2020-03-05T00:00:00", "2020-03-06T00:00:00", "2020-03-07T00:00:00", "2020-03-08T00:00:00", "2020-03-09T00:00:00", "2020-03-10T00:00:00", "2020-03-11T00:00:00", "2020-03-12T00:00:00", "2020-03-13T00:00:00", "2020-03-14T00:00:00", "2020-03-15T00:00:00", "2020-03-16T00:00:00", "2020-03-17T00:00:00", "2020-03-18T00:00:00", "2020-03-19T00:00:00", "2020-03-20T00:00:00", "2020-03-21T00:00:00", "2020-03-22T00:00:00", "2020-03-23T00:00:00", "2020-03-24T00:00:00", "2020-03-25T00:00:00", "2020-03-26T00:00:00", "2020-03-27T00:00:00", "2020-03-28T00:00:00", "2020-03-29T00:00:00", "2020-03-30T00:00:00", "2020-03-31T00:00:00")

youth_april <- c("2020-04-01T00:00:00", "2020-04-02T00:00:00", "2020-04-03T00:00:00", "2020-04-04T00:00:00", "2020-04-05T00:00:00", "2020-04-06T00:00:00", "2020-04-07T00:00:00", "2020-04-08T00:00:00", "2020-04-09T00:00:00", "2020-04-10T00:00:00", "2020-04-11T00:00:00", "2020-04-12T00:00:00", "2020-04-13T00:00:00", "2020-04-14T00:00:00", "2020-04-15T00:00:00", "2020-04-16T00:00:00", "2020-04-17T00:00:00", "2020-04-18T00:00:00", "2020-04-19T00:00:00", "2020-04-20T00:00:00", "2020-04-21T00:00:00", "2020-04-22T00:00:00", "2020-04-23T00:00:00", "2020-04-24T00:00:00", "2020-04-25T00:00:00", "2020-04-26T00:00:00", "2020-04-27T00:00:00", "2020-04-28T00:00:00", "2020-04-29T00:00:00", "2020-04-30T00:00:00")

youth_may <- c("2020-05-01T00:00:00", "2020-05-02T00:00:00", "2020-05-03T00:00:00", "2020-05-04T00:00:00", "2020-05-05T00:00:00", "2020-05-06T00:00:00", "2020-05-07T00:00:00", "2020-05-08T00:00:00", "2020-05-09T00:00:00", "2020-05-10T00:00:00", "2020-05-11T00:00:00", "2020-05-12T00:00:00", "2020-05-13T00:00:00", "2020-05-14T00:00:00", "2020-05-15T00:00:00", "2020-05-16T00:00:00", "2020-05-17T00:00:00", "2020-05-18T00:00:00", "2020-05-19T00:00:00", "2020-05-20T00:00:00", "2020-05-21T00:00:00", "2020-05-22T00:00:00", "2020-05-23T00:00:00", "2020-05-24T00:00:00", "2020-05-25T00:00:00", "2020-05-26T00:00:00", "2020-05-27T00:00:00", "2020-05-28T00:00:00", "2020-05-29T00:00:00", "2020-05-30T00:00:00", "2020-05-31T00:00:00")

youth_june <- c("2020-06-01T00:00:00", "2020-06-02T00:00:00", "2020-06-03T00:00:00", "2020-06-04T00:00:00", "2020-06-05T00:00:00", "2020-06-06T00:00:00", "2020-06-07T00:00:00", "2020-06-08T00:00:00")

# Filters the data by Occupancy Date
youth_Jan_shelter <- shelterByYouth %>%
  filter(as.character(OCCUPANCY_DATE) %in% youth_january)

youth_Feb_shelter <- shelterByYouth %>%
  filter(as.character(OCCUPANCY_DATE) %in% youth_february)

youth_March_shelter <- shelterByYouth %>%
  filter(as.character(OCCUPANCY_DATE) %in% youth_march)

youth_April_shelter <- shelterByYouth %>%
  filter(as.character(OCCUPANCY_DATE) %in% youth_april)

youth_May_shelter <- shelterByYouth %>%
  filter(as.character(OCCUPANCY_DATE) %in% youth_may)

youth_June_shelter <- shelterByYouth %>%
  filter(as.character(OCCUPANCY_DATE) %in% youth_june)



#gg-plots on a month by month basis:
youth_Jan_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

youth_Feb_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

youth_March_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

youth_April_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

youth_May_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

youth_June_shelter %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())
```





```{r echo = FALSE}
#STUFF ALEX SENT THROUGHT GITHUB
=======
install.packages("lmtest")
library(lmtest)

>>>>>>> 289b33cdd462585a63f7d4d5133906d9bbc49017
shelterDataSub <- shelterData %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  filter(as.character(SECTOR) == "Women" | as.character(SECTOR) == "Men" &
           as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  select(OCCUPANCY_DATE, SECTOR, CAPACITY, OCCUPANCY, SHELTER_CITY, relaFreq)
# removes all NaNs caused by zero capacity values 
shelterDataSub <- shelterDataSub[!(shelterDataSub$CAPACITY == 0), ] 
<<<<<<< HEAD



shelterModel <- glm(as.factor(relaFreq) ~ SECTOR + SHELTER_CITY, 
                 data=shelterDataSub, family=binomial(link='logit'))
summary(shelterModel)
=======
# shelterModel <- glm(relaFreq ~ SECTOR + ORGANIZATION_NAME, 
#                  data=shelterDataSub, family=binomial)
# 
# knitr::kable(summary(shelterModel)$coef, digits=3)
# 
# logOdds <- cbind(est = shelterModel$coef, confint(shelterModel, level = 0.95))
# odds <- exp(logOdds)
# odds[1,] <- odds[1,] / (1+odds[1,])
# 
# 
# knitr::kable(odds, digits=3)
# 
# summary(shelterModel)
>>>>>>> 289b33cdd462585a63f7d4d5133906d9bbc49017

shelterModel2 <- glm(OCCUPANCY ~ SECTOR + CAPACITY + SHELTER_CITY, data = shelterDataSub, family = poisson(link = "log"))

<<<<<<< HEAD
logOdds <- cbind(est = shelterModel$coef, confint(shelterModel, level = 0.95))
odds <- exp(logOdds)
odds[1,] <- odds[1,] / (1+odds[1,])
rownames(odds)[1] = 'Baseline prob'
=======
logRate <- cbind(est=shelterModel2$coef, confint(shelterModel2, level=0.99))

summary(shelterModel2)
knitr::kable(cbind(summary(shelterModel2)$coef,exp(logRate)),digits=3)
>>>>>>> 289b33cdd462585a63f7d4d5133906d9bbc49017

shelterDataSub$SECTOR <- factor(shelterDataSub$SECTOR, ordered = FALSE)
shelterDataSub$SHELTER_CITY <- factor(shelterDataSub$SHELTER_CITY, ordered = FALSE)

<<<<<<< HEAD

```




```{r echo=FALSE}
#STUFF ALEX SENT ME THROUGH FB:
shelterDataSub <- shelterData %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  filter(as.character(OCCUPANCY_DATE) > "2020-03-17T00:00:00") #& as.character(SECTOR) == "Women" | as.character(SECTOR) == "Men" | as.character(SECTOR) == "Co-ed" | as.character(SECTOR) == "Families" | as.character("Youth"))
# removes all NaNs caused by zero capacity values (ARE YOU REFERRING TO THE #&????)
shelterDataSub <- shelterDataSub[!(shelterDataSub$CAPACITY == 0), ] 
#Commented out your model below, beacuse I believe its not the one we want.
#shelterModel <- glm(relaFreq ~ SECTOR + ORGANIZATION_NAME, 
                 #data=shelterDataSub, family=binomial)
knitr::kable(summary(shelterModel)$coef, digits=3)
logOdds <- cbind(est = shelterModel$coef, confint(shelterModel, level = 0.95))
odds <- exp(logOdds)
odds[1,] <- odds[1,] / (1+odds[1,])
knitr::kable(odds, digits=3)
summary(shelterModel)
#Below is the model I believe we want
shelterModel2 <- glm(OCCUPANCY ~ SECTOR + CAPACITY+SHELTER_CITY, data = shelterDataSub, family = poisson(link = "log"))
summary(shelterModel2)
#My Work:
#Question: What Covariates do I want to add onto Alex's model? Play around with them a bit and see what significant values I get. This I will be able to determine from the p-values (the smaller they are the better). Next I will want to be able to interrupt the data. Most importantly, be able to determine what the intercept and coefficients tell us. Then I will want to determine a confidence interval both around the model, and the response variable (I think?). Look at past 302 notes to see where I did the confidence intervals around. KEEP IN MIND WE ARE DEALING WITH COUNT NOW, AND NO LONGER FREQUENCY!


count_shelterdata <- shelterData$SHELTER_CITY

#the POSSIBLE covariates are: "X_id", "OCCUPANCY_DATE", "SECTOR", "SHELTER_POSTAL_CODE", "CAPACITY", "SHELTER_PROVINCE", "FACILITY_NAME", "SHELTER_NAME", "OCCUPANCY", "ORGANIZATION_NAME", "SHELTER_ADDRESS", "SHELTER_CITY", "PROGRAM_NAME", "id", "DateRange", "relaFreq"

#Looking at the summary of shelterModel2 it can be seen that both the covariate Sector, Capacity and Shelter Location are important, because they have VERY small p-values.

#Me Playing Around With Different Models:
shelterModel2_mine <- glm(OCCUPANCY ~ SECTOR + CAPACITY + SHELTER_CITY + CAPACITY*SHELTER_CITY, data = shelterDataSub, family = poisson(link = "log"))
#When this interactive variable is added in (i.e CAPACITY*SHELTER_CITY), the sector: men no longer becomes significant (i.e it has a p-values of 0.11)
summary(shelterModel2_mine)
```
=======
# need a better criteria for selecting a baseline
shelterDataSub$category <- relevel(shelterDataSub$SECTOR, 'Men')
shelterDataSub$city <- relevel(shelterDataSub$SHELTER_CITY, 'Toronto')
# I still think an offset is required to give a proper "rate" value. Possible solution is to divide current occupancy by 
# previous occupancy to return a percent change in occupancy per day?
shelterModel3 <- glm(OCCUPANCY ~ sectorCat + CAPACITY*city, data = shelterDataSub, family = poisson(link = "log"))
logRate2 <- cbind(est=shelterModel3$coef, confint(shelterModel3, level=0.99))
knitr::kable(cbind(summary(shelterModel3)$coef,exp(logRate2)),digits=3)

lmtest::lrtest(shelterModel2, shelterModel3)

```
The generalised linear model follows a Poisson regression with a log link, where the response represents the number of homeless clients in a shelter on that day.
The covariates in the model are: SECTOR (categorization of the type of residents from "Men", "Women", "Families", "Co-ed" and "Youth"), SHELTER_CITY (the city of the shelter locations from "Toronto", "North York", "Scarborough" and "Etobicoke"), and CAPCITY (the maximum number of beds available for the residents). 

The baseline represents the number of male homeless clients who are visiting a Toronto shelter. 

From the table above, we can see that the number of clients who are Co-ed in Toronto shelters are similar to the number of male clients in Toronto shelters (P-value > 0.05).

As seen from a small p-value, it is evident that model including the interaction between capacity and shelter city explains the data significantly more accurately. This is likely the result of some cities, such as Toronto, containing much larger facilities with higher capacity than other cities such as Scarborough and North York. 
>>>>>>> 289b33cdd462585a63f7d4d5133906d9bbc49017



<<<<<<< HEAD
=======
```
>>>>>>> 289b33cdd462585a63f7d4d5133906d9bbc49017
