---
title: "DataFest 2020 Project"
author: "Jonas"
date: "09/06/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r pressure, echo=FALSE}
# Go to thhis html link: "https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=2110001901&pickMembers%5B0%5D=2.5&pickMembers%5B1%5D=4.1"
#After proceed to download the download csv options, and download the csv that states "Download entire table "Monthly survey of food services and drinking places""

library(shiny)
library(shinydashboard)
library(tidyverse)

#Reading the csv now:
alcohol_drinking_places <- read.csv("21100019.csv")
attach(alcohol_drinking_places)

#Assume a signifigance level of 0.05 (possibly change it?)

#$H_{0}$: COVID-19 did not impact alcohol comsumption in Canada
#$H_{1}$: COVID-19 impacted alcohol consumption in Canada

#TO determine what the graphs look like and how to work them from here

boxplot(value, main = "Boxplot to determine the sales prices")

summary(alcohol_drinking_places)

ggplot(alcohol_drinking_places$value)

qqnorm(alcohol_drinking_places$value)

qqline(alcohol_drinking_places$value)

qqnorm(log10(alcohol_drinking_places$value), cex=0.5)

qqline(log10(alcohol_drinking_places$value))

qqnorm((1 / (alcohol_drinking_places$value)), cex = 0.5)

```

Signifigance level: 0.05 (#change it?)
Assumptions: $^{1)}$The first case of COVID-19 appeared in the month of November
             $^{2)}$ For the purpose of this report, "CORONAVIRUS/COVID-19 MONTHS" will be from                the months of November 2019 until now
             $^{3)}$ Pre COVID-19 refers to the time before November 1st 2019  


First null hypothesis is: COVID-19 did not create a change on alcohol consumption
First Alternative hypothesis: COVID-19 did create a change on alcohol consumption

Second hypothesis is: There has been no change in alcohol consumpition throughout the months of COVID-19
Second Alternative hypothesis: There has been a change in alcohol consumption throughout the months of COVID-19


