---
title: "DataFest 2020 - Homeless"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r message = FALSE, echo = FALSE}
library(shiny)
library(shinydashboard)
library(tidyverse)
library(ggplot2)

#Reading the csv
shelterData <- read.csv("https://raw.githubusercontent.com/alexminsung/ISSC/master/data/Daily%20shelter%20occpancy%20current.csv?token=APUVSRCQBS7QDHDGTMGCLMS65JGQU")
attach(shelterData)

shelterData %>% 
  distinct(SHELTER_NAME)

# Finds all rows that starts witih "HFS"
HFS <- grep("^HFS", as.character(shelterData$SHELTER_NAME), value = TRUE)

# List of shelters with COVID19 cases
target <- c("COSTI Reception Centre", "Seaton House", HFS, "Salvation Army - Maxwell Meighen", 
            "SVDP - Mary's Home", "Robertson House")

# Filters the data by reported Covid19 cases
shelterByCovid <- shelterData %>%
  filter(as.character(SHELTER_NAME) %in% target)
  



```

Qs: The effects of covid19 on homeless shelters/homeless?
- but how does an increase in occupancy in shelter a impact the society (societal impact)?
- the numbers are obviously going to increase because non-essential travels are restricted and homeless are more likely to be in shelters
- there are possible health impacts...

1. try to sort the data to include 14 days period before the reported case
2. (if possible) compare it to the reported case around the region at the time of the reported case (or couple days after)
  - want to see if these shelters acted as a hotspot


```{r echo = FALSE}
#I have separated the data by sector as you suggested but even then the points are very messy. If you can think of a way to 
# improve this, then go ahead

# from this we can see that men and women make up most of the data (maybe we can exclude the rest?)
shelterData %>%
  filter(as.character(SECTOR) == "Co-ed") %>%
  summarise(n())
shelterData %>%
  filter(as.character(SECTOR) == "Families") %>%
  summarise(n())
shelterData %>%
  filter(as.character(SECTOR) == "Men") %>%
  summarise(n())
shelterData %>%
  filter(as.character(SECTOR) == "Women") %>%
  summarise(n())
shelterData %>%
  filter(as.character(SECTOR) == "Youth") %>%
  summarise(n())

shelterData %>%
  filter(as.character(SECTOR) == "Co-ed" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) +
  geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())

shelterData %>%
  filter(as.character(SECTOR) == "Families" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) +     geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())


shelterData %>%
  filter(as.character(SECTOR) == "Women" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) +   geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())


shelterData %>%
  filter(as.character(SECTOR) == "Men" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) +   geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())


shelterData %>%
  filter(as.character(SECTOR) == "Youth" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) +   geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())

  
```

```{r echo = FALSE}
# this is on the side, since i wanted to see if the numbers dropped after a covid19 case was reported on some of these shelters
shelterByCovid %>%
  filter(as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00" & as.character(ORGANIZATION_NAME) == "Homes First Society") %>%
  mutate(log_occupancy = log(OCCUPANCY)) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + geom_point() + 
  facet_wrap(~ORGANIZATION_NAME) +
  geom_vline(aes(xintercept = as.character(OCCUPANCY_DATE) == "2020-05-22T00:00:00"), color="black", linetype="dashed") + 
  theme(axis.text.x = element_text(angle=90, hjust=0))

```



"hello"