---
title: "DataFest 2020 - Homeless"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r message = FALSE, echo = FALSE}
library(shiny)
library(shinydashboard)
library(tidyverse)
library(ggplot2)

#Reading the csv
shelterData <- read.csv("https://raw.githubusercontent.com/alexminsung/ISSC/master/data/Daily%20shelter%20occpancy%20current.csv?token=APUVSRCQBS7QDHDGTMGCLMS65JGQU")
attach(shelterData)

# shelterData %>% 
#   distinct(SHELTER_NAME)

# Finds all rows that starts witih "HFS"
HFS <- grep("^HFS", as.character(shelterData$SHELTER_NAME), value = TRUE)

# List of shelters with COVID19 cases
target <- c("COSTI Reception Centre", "Seaton House", HFS, "Salvation Army - Maxwell Meighen", 
            "SVDP - Mary's Home", "Robertson House")

# Filters the data by reported Covid19 cases
shelterByCovid <- shelterData %>%
  filter(as.character(SHELTER_NAME) %in% target)

```

Qs: The effects of covid19 on homeless shelters/homeless?
- but how does an increase in occupancy in shelter a impact the society (societal impact)?
- the numbers are obviously going to increase because non-essential travels are restricted and homeless are more likely to be in shelters
- there are possible health impacts...

1. try to sort the data to include 14 days period before the reported case
2. (if possible) compare it to the reported case around the region at the time of the reported case (or couple days after)
  - want to see if these shelters acted as a hotspot


```{r echo = FALSE}
#I have separated the data by sector as you suggested but even then the points are very messy. If you can think of a way to 
# improve this, then go ahead


shelterData %>%
  filter(as.character(SECTOR) == "Co-ed" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = relaFreq, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

shelterData %>%
  filter(as.character(SECTOR) == "Women" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = relaFreq, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

shelterData %>%
  filter(as.character(SECTOR) == "Men" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = relaFreq, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

shelterData %>%
  filter(as.character(SECTOR) == "Families" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = relaFreq, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

shelterData %>%
  filter(as.character(SECTOR) == "Youth" & as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00") %>%
  mutate(relaFreq = OCCUPANCY/CAPACITY) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = relaFreq, color = SHELTER_NAME)) + facet_wrap(SHELTER_CITY~ORGANIZATION_NAME) + geom_point() + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 

  
```

```{r echo = FALSE}
# this is on the side, since i wanted to see if the numbers dropped after a covid19 case was reported on some of these shelters
shelterByCovid %>%
  filter(as.character(OCCUPANCY_DATE) > "2020-03-01T00:00:00" & as.character(ORGANIZATION_NAME) == "Homes First Society"
         & as.character(SECTOR) == "Women") %>%
  mutate(log_occupancy = log(OCCUPANCY)) %>%
  ggplot(aes(x = OCCUPANCY_DATE, y = OCCUPANCY, color = SHELTER_NAME)) + geom_point() + 
  facet_wrap(~ORGANIZATION_NAME) +
  geom_vline(aes(xintercept = '2020-04-09T00:00:00'), color="black", linetype="dashed") + 
  geom_vline(aes(xintercept = '2020-03-17T00:00:00'), color="red", linetype="dashed") +
  #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 
  theme(axis.text.x = element_text(angle=90, hjust=0))

```

Unlike our previous hypothesis, comparing the occupancy of Women shelters around Scarborough and Toronto have shown either a general decrease in numbers or minimal changes at best. Only one stands as an exception to this, which is the Home First Society Women's sector, where there have been a slight increase in numbers ever since Toronto's lock-down on March 17  (indicated by a red line). However, even this facility shows to illustrate a much steeper decrease around April 21st. 

I believe that this sudden decrease is likely contributed by the emergence of mass infections which occurred at the Homes First Shelter - Willowdale Welcome Center on the 9th of April. Considered as the "largest COVID-19 outbreak in the city's shelter system" by Toronto Star (https://www.thestar.com/news/gta/2020/05/24/how-a-haven-for-refugees-became-home-to-the-worst-covid-19-outbreak-in-torontos-shelter-system.html), it is no doubt that this foreboding news caught the attention of many residents in other shelters. While without solid evidence, I believe such news could have instilled fears among the residents in other Home First Society affiliated shelters, possibly providing a sufficient explanation in the sudden dip in occpancy. 


The spread characteristic of the virus could be another factor which possibly explains the decrease/little change in occupancy in shelters. As the virus is infamous for being easily contagious, it is possible that those without homes may have preferred to stay isolated from places with large crowds (i.e. shelters). This hypothesis is supported by the steadily declining numbers in occupancy at many shelters ever since COVID-19 was declared a pandemic. 


```{r echo = FALSE}

install.packages("lmtest")
library(lmtest)

shelterDataSub <- shelterData %>%
  filter(as.character(OCCUPANCY_DATE) > "2020-03-17T00:00:00") #& as.character(SECTOR) == "Women" | as.character(SECTOR) == "Men") 

# removes all NaNs caused by zero capacity values 
shelterDataSub <- shelterDataSub[!(shelterDataSub$CAPACITY == 0), ] 
# shelterModel <- glm(relaFreq ~ SECTOR + ORGANIZATION_NAME, 
#                  data=shelterDataSub, family=binomial)
# 
# knitr::kable(summary(shelterModel)$coef, digits=3)
# 
# logOdds <- cbind(est = shelterModel$coef, confint(shelterModel, level = 0.95))
# odds <- exp(logOdds)
# odds[1,] <- odds[1,] / (1+odds[1,])
# 
# 
# knitr::kable(odds, digits=3)
# 
# summary(shelterModel)

shelterModel2 <- glm(OCCUPANCY ~ SECTOR + CAPACITY + SHELTER_CITY, data = shelterDataSub, family = poisson(link = "log"))

logRate <- cbind(est=shelterModel2$coef, confint(shelterModel2, level=0.99))

summary(shelterModel2)
knitr::kable(cbind(summary(shelterModel2)$coef,exp(logRate)),digits=3)

shelterDataSub$SECTOR <- factor(shelterDataSub$SECTOR, ordered = FALSE)
shelterDataSub$SHELTER_CITY <- factor(shelterDataSub$SHELTER_CITY, ordered = FALSE)

# need a better criteria for selecting a baseline
shelterDataSub$category <- relevel(shelterDataSub$SECTOR, 'Men')
shelterDataSub$city <- relevel(shelterDataSub$SHELTER_CITY, 'Toronto')
# I still think an offset is required to give a proper "rate" value. Possible solution is to divide current occupancy by 
# previous occupancy to return a percent change in occupancy per day?
shelterModel3 <- glm(OCCUPANCY ~ category + CAPACITY*city, data = shelterDataSub, family = poisson(link = "log"))
logRate2 <- cbind(est=shelterModel3$coef, confint(shelterModel3, level=0.95))
knitr::kable(cbind(exp(logRate2)),digits=3)

lmtest::lrtest(shelterModel2, shelterModel3)

```
The generalised linear model follows a Poisson regression with a log link, where the response represents the number of homeless clients in a shelter on that day.
The covariates in the model are: SECTOR (categorization of the type of residents from "Men", "Women", "Families", "Co-ed" and "Youth"), SHELTER_CITY (the city of the shelter locations from "Toronto", "North York", "Scarborough" and "Etobicoke"), and CAPCITY (the maximum number of beds available for the residents). 

The baseline represents the number of male homeless clients who are visiting a Toronto shelter. 

From the table above, we can see that there are more male clients in Toronto shelters than Women or Youth but less than families and co-ed clients in Toronto shelters. This is likely because these clients are considered at least pairs in numbers.

Furthermore, considering the capacity estimate is greater than 1, we can deduce that most shelters have not been filled to their full capacity. This coincides with the earlier graph showing a general decrease in occupancy as time progressed and such behavior may be attributed to the increasing cases of COVID-19 in shelters. Such trend is also present when exploring the interactions between capacities and cities which implies that shelters in other cities also have vacant rooms/beds. 

Unsurprisingly, the table also illustrates that there are greater number of clients in Toronto areas than its surrounding cities. 

As seen from a small p-value, it is evident that model including the interaction between capacity and shelter city explains the data significantly more accurately. This is likely the result of some cities, such as Toronto, containing much larger facilities with higher capacity than other cities such as Scarborough and North York. 

```{r echo = FALSE}
#install.packages("gamm4")
library(gamm4)
time <- as.character(shelterDataSub$OCCUPANCY_DATE)
gamm4(relaFreq ~ SECTOR + SHELTER_CITY + s(OCCUPANCY_DATE), data=shelterDataSub, family=binomial(link='logit'))


```